Crossing Origins by Crossing Formats

### 2012-11-01 main.tex
slight restructuring
Updated section Crossing origins

@@

\section{Introduction}
\label{sec:intro}

What and how?

\subsection{Exploiting polyglots}

A polyglot can be used for exploitation if there is a difference between how 
content is interpreted at the time of verification compared to time of use. 
It is possible to create such a polyglot by mixing content, that is benign when verified, with content, that is 
malicious when executed. The verification process will see the benign content 
and allow it, but subsequently the malicious content is executed.

\subsection{Syntax injection attacks}

@@

\subsection{Polyglot upload attacks}

@@

\subsection{Crossing origins by crossing formats}

Describe how the attacks lead to Same-Origin Policy bypass.

\subsubsection{Syntax injection scenario}

Description of attack technique

Attack building blocks

\subsubsection{Polyglot upload scenario}

Description of attack technique

Building blocks

\section{Vulnerabilities}

@@

[anything] \%PDF- [anything] \
[ anything ] [space] trailer [space] << [any name value pair] 
/Root [space ] <<[any name value pair] /Pages [space]<< [any name value pair] >> [any name value pair] >> [any name value pair] >>

@@

\section{Evaluation}

@@

This effectively bypasses any cross-site scripting filters such as 
NoScript or filters built into browsers. Since the Reader plugin 
handles the response, the broser never gets to see the content

@@

\section{Prevention}

@@

Sever content from a sandbox domain.

@@

\section{Related work}

\section{Conclusions}

\bibliographystyle{IEEEtran}
\bibliography{literature}

>>>>

\usepackage{listings}

@@

%1 pages
\section{Introduction}
\label{sec:intro}

General introduction for web application security.

The following attacks have  been particularly successful (support with references).

\subsection{Injection attacks}

@@

\subsection{Content repurposing attacks}

@@

Bridge to the next session saying that we take these attacks to the
next level.

%3 pages
\section{Crossing origins by crossing formats}

% Describe how the attacks lead to Same-Origin Policy bypass.

In this section we generalize the problem and describe 
how it can be abused to circumvent the same-origin policy.

% What and how?

A polyglot is defined as ``A person who knows several languages.'', 
and the term is widely used in various fields of science. In computer 
science, a polyglot is a program that is valid in multiple programming 
languages. In this paper we use a broader definition of a programming language, 
not limited to code meant for compilation to machine code or scripting 
languages, but extended to any format that requires interpretation 
before rendering.

A polyglot is composed from various constructs that are either 
common between languages; or constructs that are language specific, but carrying 
different meaning in each language. To maintain validity across languages, 
one must ensure that language specific constructs are not interpreted by 
other languages. This is often accomplished by hiding the parts of the 
code specific to one language, in parts interpreted as comments or text 
of another.

Certain languages are particularly suitable for creating polyglots. 
These languages either have a lot of constructs in common with other 
languages, such as \emph{C}, or are defined such that the parser 
ignores that which it cannot interpret, such as \emph{HTML}. The 
latter allows for ample opportunity to hide any code specific to 
another language, as long as there is no overlap with the syntax 
of the first language.

\subsection{Malicious polyglots}

A polyglot can be used for malicious purposes if there is a difference 
between the expected execution environment and the actual environment 
it is executed in.
In the situation where

at the time of verification compared to time of use

It is possible to create such a polyglot by mixing content, that is benign 
when verified, with content, that is 
malicious when executed. The verification process will see the benign content 
and allow it, but subsequently the malicious content is executed.

\subsection{Syntax injection}

% Description of attack technique

In a cross-site scripting attack, HTML syntax is injected into a 
preexisting HTML document via vulnerable user supplied parameters. Similarly, 
a syntax injection attack consists of injecting foreign syntax into 
preexisting content of a different format, thereby creating a polyglot.
The polyglot content can then be interpreted as either format; the benign 
original format, or the malicious user-supplied format.

% Attack building blocks

For this attack to be successful certain requirements needs to be 
fulfilled. 
\begin{itemize}
	\item The original content must include parameters under the control of the 
				user.
	\item The user-supplied content must circumvent any validation or filtering.
	\item There must exist a way of coercing the resulting polyglot to be 
				interpreted as the malicious format.
	\item The malicious format must have capabilities that are restricted or 
				missing in the benign format.
\end{itemize}

% Scenarios

Much like a cross-site scripting attack, we consider a scenario where a website serves documents which are based upon user-supplied content.

The same-origin policy is intended to prevent a document from one origin from accessing the content of a document of another origin. At the same time it allows a script-tag in one document to include JavaScript of another origin and execute it in the context of that document. If an attacker is able to inject an HTML-document with JavaScript syntax in such a way that it became valid JavaScript, the attacker could include the document across origins via a script-tag and extract its content, thereby circumventing the same-origin policy.

Consider the php-program in listing \ref{lst:php-sample}. Apart from being vulnerable to traditional cross-site scripting, it is vulnerable

By requesting the site with parameter $guess=</body></html>;x=<html><body>$, the resulting document, listing \ref{lst:html-js}, is both malformed but valid HTML and valid JavaScript in browsers that support E4X. An attacker can now include the page as a script in the attackers page and extract the secret from variable x.

\begin{lstlisting}[label=lst:php-sample,caption=Vulnerable PHP-program,captionpos=b]
<?php
session_start();
$_SESSION["secret"] = rand();
?>
<html><body>
Your guess: <?=$_GET["guess"]?>!
The secret is: <?=$_SESSION["secret"]?>
</body></html>
\end{lstlisting}
\begin{lstlisting}[label=lst:html-js,caption=Vulnerable PHP-program,captionpos=b]
<html><body>
Your guess: </body></html>;x=<html><body>!
The secret is: 521352342
</body></html>
\end{lstlisting}$

This attack has been suggested as a way to bypass Content Security Policy. As E4X is only supported in the SpiderMonkey JavaScript engine, used in Firefox, this limits the exploitability of this scenario.
While this is an unlikely scenario using JavaScript as the injected format, section \ref{sec:vuln} will show how this can be achieved in practice.

\subsection{Content repurposing}

% Description of attack technique
A content repurposing attack attacks a service that accepts and serves user supplied files. The files are verified to be of a certain benign file type, e.g. an image, before being served to the end user. By submitting a polyglot to such a service, an attacker can trick the service into serving malicious content under the origin of the service. The service can verify the

% Building blocks
For this attack to be successful certain requirements needs to be 
fulfilled.

\begin{itemize}
	\item The service must accept and serve user-supplied files.
	\item The service must verify the user-supplied polyglot as the benign 
				format.
	\item There must exist a way of coercing the polyglot to be 
				interpreted as the malicious format.
\end{itemize}

% Scenarios

%3 pages
\section{Vulnerabilities}
\label{sec:vuln}

@@

[anything] \%PDF- [anything] \
[ anything ] [space] trailer [space] << [any name value pair] 
/Root [space] <<[any name value pair] /Pages [space]<< [any name value pair] 
>> [any name value pair] >> [any name value pair] >>

@@

%3 pages
\section{Evaluation}

@@

This effectively bypasses any cross-site scripting filters such as 
NoScript or filters built into browsers. Since the Reader plug-in 
handles the response, the browser never gets to see the content

@@

%1-2 pages
\section{Mitigation}

@@

Serve content from a sandbox domain.

@@

%1 page
\section{Related work}

%1 page
\section{Conclusions}

We have contacted the vendors...

Mentioned that Adobe was notified long time ago.

%1-2 pages
\bibliographystyle{IEEEtran}
\bibliography{literature}
